Paper Figure Generation

### 2023-08-08 R/PaperFigureGeneration.rmd
Updates to feature relative and correlation figs

@@

>>>>

```{r read_figure_7_data}
set.seed(8785)
NHF1PairedCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
NHF1ShuffledCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
for (i in seq_along(NHF1PairedCutSiteDistances)) {
  NHF1PairedCutSiteDistances[[i]] = list(CC_to_TT = NULL, C_to_T = NULL, non_C_to_T = NULL)
  NHF1PairedCutSiteDistances[[i]]$CC_to_TT = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "CC>TT"
  ))
  NHF1ShuffledCutSiteDistances[[i]] = getShufflePairedCutSiteDistances(NHF1PairedCutSiteDistances[[i]]$CC_to_TT)

  NHF1PairedCutSiteDistances[[i]]$C_to_T = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T"
  ))

  NHF1PairedCutSiteDistances[[i]]$non_C_to_T = fread(generateFilePath(
    NHF1CutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1PairedCutSiteDistances)[i],
    repitition = "all_reps", filtering = "TGG_filtered",
    omittedMismatches = "C>T"
  ))
}

```{r figure_7A, fig.width = 6, fig.height = 5}
print(paste0("Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12, 26), ylim = c(18.5, 32.5), xAxisBreaks = seq(13,25,3))
```
```{r figure_7B, fig.width = 6, fig.height = 5}
print(paste0("Read Length SLope: ", getReadLengthSlope(NHF1ShuffledCutSiteDistances$`1h`)))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, READ_LENGTH,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(6,30), ylim = c(13,37))
```
```{r figure_7C, fig.width = 6, fig.height = 5}
print(paste0("Read length slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, READ_LENGTH,
                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
                           xlim = c(0,31), ylim = c(15,31))
```
```{r figure_7D, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7E, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1ShuffledCutSiteDistances$`1h`)*-100, '%'))
plotPairedCutSiteDistances(NHF1ShuffledCutSiteDistances$`1h`, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h CC>TT All Reps TGG-filtered Shuffled",
                           xlim = c(12,26), ylim = c(0,14.5),
                           xAxisBreaks = seq(12,26,2), yAxisBreaks = seq(0,14,2))
```
```{r figure_7F, fig.width = 6, fig.height = 5}
print(paste0("Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$non_C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$non_C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h Non-C>T All Reps TGG-filtered",
                           xlim = c(0,31), ylim = c(0,31))
```

```{r read_figure_8_data}
NHF1NucleosomeRelativeCutSiteDistances = list(`1h` = NULL, `8h` = NULL)
for (i in seq_along(NHF1NucleosomeRelativeCutSiteDistances)) {
  NHF1NucleosomeRelativeCutSiteDistances[[i]] = list(three_prime = NULL, five_prime = NULL)
  NHF1NucleosomeRelativeCutSiteDistances[[i]]$three_prime = fread(generateFilePath(
    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
    strandPolarity = THREE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
  ))
  NHF1NucleosomeRelativeCutSiteDistances[[i]]$five_prime = fread(generateFilePath(
    NHF1FeatureRelativeDataDirectory, dataTypeStrings$featureRelativeMeanCutSiteDistance, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1NucleosomeRelativeCutSiteDistances)[i],
    strandPolarity = FIVE_PRIME, repitition = "all_reps", filtering = "TGG_filtered",
    includedMismatches = "C>T", additionalInformation = "hg19_mnase_all_related_strand_aligned"
  ))
}
```

```{r figure_8A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          plotCutSiteSignificance = FALSE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_8B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_8C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`1h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 1h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          mainYAxisMin = 7.08, mainYAxisBreaks = seq(7.1,7.8,0.1),
                          secondaryAxisBreaks = seq(19,19.8,0.2), 
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```

@@

```{r figure_S13, fig.width = 6, fig.height = 5}
print(paste0("1h C>T Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`1h`$C_to_T)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, READ_LENGTH,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("1h C>T Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`1h`$C_to_T)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`1h`$C_to_T, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 1h C>T All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))

print(paste0("8h CC>TT Read Length Slope: ", getReadLengthSlope(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, READ_LENGTH,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5, 26.5), ylim = c(17.5, 33.5),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(18,33,3))
print(paste0("8h CC>TT Coupling: ", getCouplingRate(NHF1PairedCutSiteDistances$`8h`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(NHF1PairedCutSiteDistances$`8h`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "NHF1 8h CC>TT All Reps TGG-filtered",
                           xlim = c(10.5,26.5), ylim = c(0,16),
                           xAxisBreaks = seq(11,26,3), yAxisBreaks = seq(0,15,3))
```

```{r read_figure_S14_data}
yeastPairedCutSiteDistances = list(`20min` = NULL)
yeastPairedCutSiteDistances$`20min` = list(CC_to_TT = NULL, non_C_to_T = NULL)
yeastPairedCutSiteDistances$`20min`$CC_to_TT = fread(generateFilePath(
  yeastCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", filtering = "TGG_filtered",
  includedMismatches = "CC>TT"
))

arabidopsisPairedCutSiteDistances = list(ZT2 = NULL)
arabidopsisPairedCutSiteDistances$ZT2 = list(CC_to_TT = NULL, non_C_to_T = NULL)
arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT = fread(generateFilePath(
  arabidopsisCutSiteCorrelationDirectory, dataTypeStrings$pairedCutSiteDistances , ".tsv",
  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
  repitition = "all_reps", filtering = "TGG_filtered",
  includedMismatches = "CC>TT"
))

```{r figure_S14, fig.width = 6, fig.height = 5}
print(paste0("Arabidopsis CC>TT read length slope: ", getReadLengthSlope(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, READ_LENGTH,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(22,32), yAxisBreaks = c(23,25,27,29,31))
print(paste0("Arabidopsis CC>TT Coupling: ", getCouplingRate(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(arabidopsisPairedCutSiteDistances$ZT2$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "Arabidopsis ZT2 CC>TT All Reps TGG-filtered",
                           xlim = c(15,25), ylim = c(3,13), yAxisBreaks = c(4,6,8,10,12))

print(paste0("Yeast CC>TT read length slope: ", getReadLengthSlope(yeastPairedCutSiteDistances$`20min`$CC_to_TT)))
plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT, READ_LENGTH,
                           title = "Yeast 20min CC>TT All Reps TGG-filtered",
                           xlim = c(11,19), ylim = c(19.5,27.5), yAxisBreaks = waiver())
print(paste0("Yeast CC>TT Coupling: ", getCouplingRate(yeastPairedCutSiteDistances$`20min`$CC_to_TT)*-100, '%'))
plotPairedCutSiteDistances(yeastPairedCutSiteDistances$`20min`$CC_to_TT, THREE_PRIME_CUT_SITE_DISTANCE,
                           title = "Yeast 20min CC>TT All Reps TGG-filtered",
                           xlim = c(11,20), ylim = c(5,14),
                           xAxisBreaks = c(11,13,15,17,19), yAxisBreaks = c(5,7,9,11,13))
```

```{r figure_S15A, fig.width = 10, fig.height = 5}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          plotCutSiteSignificance = FALSE,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-200, 200),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S15B}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(-100, -40),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
```{r figure_S15C}
plotFeatureRelativeCounts(NHF1NucleosomeRelativeCutSiteDistances$`8h`$three_prime,
                          FEATURE_RELATIVE_POSITION, MEAN_THREE_PRIME_CUT_SITE_DISTANCE,
                          countsPlotColor = "red2", mainYAxisLabel = "Mean 3' Cut Site Distance",
                          meanCutSiteDistanceTable = NHF1NucleosomeRelativeCutSiteDistances$`1h`$five_prime,
                          cutSiteStrandPolarity = FIVE_PRIME, smoothMeanCutSiteDistance = FALSE,
                          title = "NHF1 8h C>T All Reps TGG-Filtered Strand-Aligned",
                          xAxisLabel = "Dyad-Relative Position", xlim = c(40, 100),
                          secondaryAxisBreaks = seq(19,19.8,0.2),
                          meanCutSiteDistanceMax = 19.825, meanCutSiteDistanceMin = 18.975)
```
